An OpenCL Implementation of Wait-Free Sets

### 2015-06-15 Docs/paper.tex
doc chg

\usepackage{times}
\usepackage{subfigure}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{algorithm}

@@

\section{Proof of Correctness}
\begin{algorithm}
  \caption{Delete all marked nodes}
  \label{alg:deleteMarkedNode}
  \begin{algorithmic}[5]
    \Function{delMarkedNodes}{startRef, nodePool}
      \State doneFlag = false;
      \While{(!doneFlag)}    
        \State [nextRef,startMark] := getPtr(startRef);
        \If{(!startMark)}
          \State [nextNextRef,nextMark] := getPtr(nextRef);
          \If{(nextMark)}
            \State casFlag = CAS(startRef:next,[nextRef,startMark],[nextNextRef,startMark]);
            \If{casFlag}
               \State freeNode(nodePool,nextRef);
            \EndIf
          \Else
            \State
            \Return true;
          \EndIf
        \Else{}
          \State
          \Return false;  
        \EndIf
      \EndWhile        
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{theorem}
  If multiple threads are running algorithm \ref{alg:deleteMarkedNode}, then all of them will either return false, or return same unmarked nextRef.
\end{theorem}
\begin{proof}
  Consider the portion of the algorithm inside the while loop. It could be seen that the algorithm is trying to update the value of startRef:next. Each thread reads startRef:next at line 4, and atomically updates it at line 8. If multiple threads are updating it, only one thread will succeed, and so all the threads will have same value of startRef:next.

  Consider also that if some thread deletes startRef. This thread will also update startRef:next, making other threads running the algorithm return false.
\end{proof}

>>>>

\usepackage{times}
\usepackage{subfigure}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{algorithm}
%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}

@@

\section{Proof of Correctness}
\begin{algorithm}
  \caption{Deletes all marked nodes beyond {\it startRef}}
  \label{alg:deleteMarkedNode}

  \begin{algorithmic}[1]
    \Require
       \Statex startRef:Reference to the node beyond which all
               marked nodes are to be deleted. 
    \Ensure
       \Statex All marked nodes beyond {\it startRef} are deleted.
       \Statex {\it nextRef} returns next unmarked node beyond {\it startRef}.  
       \Statex Returns {\it true} if all marked nodes are deleted,
               {\it false} if node referenced by {\it startRef} gets deleted.

    \Statex   
    \Function{delMarkedNodes}{startRef, nextRef\&}
      \State doneFlag = false;
      \While{(!doneFlag)}    
        \State [nextRef,startMark] := getUnmarkedRef(startRef);
        \If{(!startMark)}
          \State [nextNextRef,nextMark] := getUnmarkedRef(nextRef);
          \If{(nextMark)}
            \State status = CAS(nodePool[startRef]:next,[nextRef,startMark],[nextNextRef,startMark]);
            \If{(status = true)}
               \State freeNode(nextRef);
            \EndIf
          \Else
            \State
            \Return true;
          \EndIf
        \Else{}
          \State
          \Return false;  
        \EndIf
      \EndWhile        
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{theorem}
  A process running algorithm \ref{alg:deleteMarkedNode}, then it will either return next unmarked node after {\it startRef} in {\it nextRef}, or return {\it false}.
\end{theorem}
\begin{IEEEproof}
  The proof consists of the following parts.
  \begin{enumerate}
    \item The state of the linked list copied to internal variables {\it nextRef} and {\it nnRef} is valid as they are read simultaneously with {\it startMark} and {\it nextMark} respectively, and both these flags are checked.
    \item If this state remains valid, then CAS operation is successful.
    \item If this state is changed by any other process, this change is completely reflected in {\it startRef:next}.  
\end{enumerate} 
\end{IEEEproof}
